---
title: "Test data science avec R"
---

```{r eval=FALSE, echo=FALSE}
pacman::p_load(rgeos,rgdal,learnr,skimr,ggvis,googleVis,corrplot,
               PerformanceAnalytics,rgdal,ggmap,rgeos,
               revealjs,DT,leaflet,data.table,
               leaflet.extras,caret,rpart,ggplot2,ipred,randomForest,
               rpart.plot,class,e1071,neuralnet,nnet,devtools,
               xgboost,AUC,hydroGOF,gbm,parallel,readr,RColorBrewer,gridExtra,
               rpart,psych,rmarkdown, rpart.plot,corrplot,DT,
               BBmisc,ParamHelpers,kernlab,ranger,irace,cmaes,
               GenSA,XML,mlr,MASS,arules,
               arulesViz,sjPlot,sjmisc,pROC,readxl,tidyverse,broom,staplr,Hmisc,
               tabplot,GGally,insuranceData,dummies,fastDummies,glmnet,plotly,dplyr
               ,DiagrammeR,Ckmeans.1d.dp,caret,lubridate, magrittr,knitr, ggpubr,countrycode,pROC,verification,countrycode,shinydashboard,shiny)
```

```{r echo=FALSE, eval=FALSE}


#####  chemin relatif du dossier contenant les fichiers ######

data.path="https://dataks.bitbucket.io/ml/"
data.path="C:/Users/SHIK/Documents/GitHub/dataks.bitbucket.io/ml/"
data.path="../../../DS/data/test/"

######### choix fichier #############

files=list.files(pattern = ".Rmd")
files.excluded = c("house_price_prediction.Rmd","regression_mlr.Rmd")
files = setdiff(files, files.excluded)

######### type fichier #############

type_document=c("html_document","html")
type_document=c("revealjs::revealjs_presentation","revealjs")
type_document=c("pdf_document","pdf")
type_document=c("beamer_presentation","beamer")

####### boucle de render  ############

for (file in files){
  render(file,"html_document",
         output_file = paste0(substr(file,1,(nchar(file)-4)),".html"),
         encoding="UTF-8",
         output_dir = "html_site",
         quiet = F,
         output_options=list(self_contained=FALSE,
                             lib_dir="html_site/site_libs", toc = TRUE,toc_float = TRUE, number_sections= TRUE))
}

```


```{r}


# Create an empty header
header <- dashboardHeader()

# Create an empty sidebar
sidebar <- dashboardSidebar()

# Create an empty body
body <- dashboardBody()
```

```{r}
header <- dashboardHeader()
sidebar <- dashboardSidebar()
body <- dashboardBody()

# Create the UI using the header, sidebar, and body
ui <- dashboardPage(header, sidebar, body)

server <- function(input, output) {}

shinyApp(ui, server)
```


mise à jour automatique

```{r}
library(shiny)

server <- function(input, output, session) {
  reactive_starwars_data <- reactiveFileReader(
        intervalMillis = 1000,
        session = session,
        filePath = starwars_url,
        readFunc = function(filePath) { 
           read.csv(url(filePath))
         }
         )
    
  output$table <-   renderTable({ reactive_starwars_data()})
}

body <- dashboardBody(
  tableOutput("table")
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)
```

" Menu dynamique"
```{r}

server <- function(input, output) {
  output$task_menu <- renderMenu({
tasks <- apply(task_data, 1, function(row) { 
  taskItem(text = row[["text"]],
           value = row[["value"]])
})
dropdownMenu(type = "tasks", .list = tasks)
  })
}

header <- dashboardHeader(dropdownMenuOutput("task_menu"))

ui <- dashboardPage(header = header,
                    sidebar = dashboardSidebar(),
                    body = dashboardBody()
                    )
shinyApp(ui, server)

```


a buton  
```{r}
library("shiny")
sidebar <- dashboardSidebar(
  actionButton("click", "Update click box")
) 

server <- function(input, output) {
  output$click_box <- renderValueBox({
    valueBox(
     value = 10,
        subtitle = "Click Box"
    )
  })
}

body <- dashboardBody(
      valueBoxOutput("click_box")
 )


ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = sidebar,
                    body = body
                    )
shinyApp(ui, server)

```


counter 

```{r}


library("shiny")
sidebar <- dashboardSidebar(
  actionButton("click", "Update click box")
) 

server <- function(input, output) {
  output$click_box <- renderValueBox({
    valueBox(
     value =input$click,
        subtitle = "Click Box"
    )
  })
}

body <- dashboardBody(
      valueBoxOutput("click_box")
 )


ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = sidebar,
                    body = body
                    )
shinyApp(ui, server)

```




```{r}
library("shiny")

body <- dashboardBody(

fluidRow(box(
    width = 12,
    title = "Regular Box, Row 1",
    "Star Wars"
    )),
    
    fluidRow(box(
    width = 12,
    title = "Regular Box, Row 2",
    "Nothing but Star Wars"
    ))

# Row 1
 
# Row 2

)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)
```


Shiny 

```{r}
library("shiny")

body <- dashboardBody(
  fluidRow(
# Column 1
infoBox(
    width = 6,
    title = "Regular Box, Column 1",
    subtitle = "Gimme those Star Wars"
    ),
# Column 2
  infoBox(
    width = 6,
    title = "Regular Box, Column 2",
    subtitle = "Don't let them end"
    )
  )
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)

```

Application avec deux colonnes 

```{r}
library("shiny")

body <- dashboardBody(
  fluidRow(
# Column 1
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Column 1",
        subtitle = "Gimme those Star Wars"
      )
    ),
# Column 2
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Column 2",
        subtitle = "Don't let them end"
      )
    )
  )
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)

```


autre configuration

```{r}

```


customise css in the main file 
```{r}
library("shiny")

body <- dashboardBody(
# Update the CSS
 body <- dashboardBody(
    tags$head(
        tags$style(
            HTML('
            h3 {
    font-weight: bold;
}
            ')
        )
    )
),
  fluidRow(
    box(
      width = 12,
      title = "Regular Box, Row 1",
      "Star Wars, nothing but Star Wars"
    )
  ),
  fluidRow(
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Row 2, Column 1",
        subtitle = "Gimme those Star Wars"
    )
   ),
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Row 2, Column 2",
        subtitle = "Don't let them end"
    )
  )
 )
)

ui <- dashboardPage(
  skin = "purple",
  header = dashboardHeader(),
  sidebar = dashboardSidebar(),
  body = body)
shinyApp(ui, server)

```

add a simple icon 

```{r}
library("shiny") 

header <- dashboardHeader(
  dropdownMenu(
    type = "notifications",
    notificationItem(
      text = "The International Space Station is overhead!",
      icon = icon("coffee")
    )
  )
)
ui <- dashboardPage(header = header,
                    sidebar = dashboardSidebar(),
                    body = dashboardBody()
                    )
shinyApp(ui, server)


```


style 

```{r}
library("shiny")

body <- dashboardBody(
  tags$head(
    tags$style(
      HTML('
      h3 {
        font-weight: bold;
      }
      ')
    )
  ),
  fluidRow(
    box(
      width = 12,
      title = "Regular Box, Row 1",
      "Star Wars, nothing but Star Wars",
# Make the box red
      status = "danger"
    )
  ),
  fluidRow(
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Row 2, Column 1",
        subtitle = "Gimme those Star Wars",
# Add a star icon
        icon = icon("star")
    )
   ),
    column(width = 6,
      infoBox(
        width = NULL,
        title = "Regular Box, Row 2, Column 2",
        subtitle = "Don't let them end",
# Make the box yellow
        color = "yellow"
    )
  )
 )
)

ui <- dashboardPage(
  skin = "purple",
  header = dashboardHeader(),
  sidebar = dashboardSidebar(),
  body = body)
shinyApp(ui, server)

```

# CASE STUDY 

# Print the nasa_fireball data frame
nasa_fireball

# Examine the types of variables present
sapply(nasa_fireball, class)

# Observe the number of observations in this data frame
nrow(nasa_fireball)

# Check for missing data
sapply(nasa_fireball, anyNA)

```{r}

```

création d'un dashboard simple 

```{r}
library("shiny")
max_vel <- max(nasa_fireball$vel, na.rm = TRUE)

body <- dashboardBody(
  fluidRow(
    # Add a value box for maximum velocity
    valueBox(
      value = max_vel,
      subtitle = "Maximum pre-impact velocity", 
      icon = icon("fire")
    )
  )
)

ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)

```



Dynamics color example 

```{r}
n_us <- sum(
  ifelse(
    nasa_fireball$lat < 64.9 & nasa_fireball$lat > 19.5
      & nasa_fireball$lon < -68.0 & nasa_fireball$lon > -161.8,
    1, 0),
  na.rm = TRUE)
  
server <- function(input, output) {
  output$us_box <- renderValueBox({
    valueBox(
      value = n_us,
      subtitle = "Number of Fireballs in the US",
      icon = icon("globe"),
      color = if (n_us < 10) {
                "blue"
              } else {
              "fuchsia"
              }
    )
  })
}

body <- dashboardBody(
  fluidRow(
    valueBoxOutput("us_box")
  )
)
ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )
shinyApp(ui, server)

```

#  add a filter 

sidebar <- dashboardSidebar(
  sliderInput(
    inputId = "threshold",
    label = "Color Threshold",
    min = 0,
    max = 100,
    value = 10)
)

server <- function(input, output) {
  output$us_box <- renderValueBox({
    valueBox(
      value = n_us,
      subtitle = "Number of Fireballs in the US",
      icon = icon("globe"),
      color = if (n_us < input$threshold) {
                "blue"
              } else {
              "fuchsia"
              }
    )
  })
}


ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = sidebar,
                    body = body
                    )
shinyApp(ui, server)

```{r}

```


```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```