---
title: "Regression with R"
---

```{r eval=FALSE, echo=FALSE}
pacman::p_load(rgeos,rgdal,learnr,skimr,ggvis,googleVis,corrplot,
               PerformanceAnalytics,rgdal,ggmap,rgeos,
               revealjs,DT,leaflet,data.table,
               leaflet.extras,caret,rpart,ggplot2,ipred,randomForest,
               rpart.plot,class,e1071,neuralnet,nnet,devtools,
               xgboost,AUC,hydroGOF,gbm,parallel,readr,RColorBrewer,gridExtra,
               rpart,psych,rmarkdown, rpart.plot,corrplot,DT,
               BBmisc,ParamHelpers,kernlab,ranger,irace,cmaes,
               GenSA,XML,mlr,MASS,arules,
               arulesViz,sjPlot,sjmisc,pROC,readxl,tidyverse,broom,staplr,Hmisc,
               tabplot,GGally,insuranceData,dummies,fastDummies,glmnet,plotly,dplyr
               ,DiagrammeR,Ckmeans.1d.dp,caret,lubridate, magrittr,knitr, ggpubr,countrycode,pROC,verification,countrycode,shinydashboard,shiny)
```

```{r echo=FALSE, eval=FALSE}

#####  chemin relatif du dossier contenant les fichiers ######
data.path="https://dataks.bitbucket.io/ml/"
data.path="C:/Users/SHIK/Documents/GitHub/dataks.bitbucket.io/ml/"
data.path="../../../DS/data/test/"

######### choix fichier #############

files=list.files(pattern = ".Rmd")
files.excluded = c("house_price_prediction.Rmd","regression_mlr.Rmd")
files = setdiff(files, files.excluded)

######### type fichier #############

type_document=c("html_document","html")
type_document=c("revealjs::revealjs_presentation","revealjs")
type_document=c("pdf_document","pdf")
type_document=c("beamer_presentation","beamer")

####### boucle de render  ############

for (file in files){
  render(file,"html_document",
         output_file = paste0(substr(file,1,(nchar(file)-4)),".html"),
         encoding="UTF-8",
         output_dir = "html_site",
         quiet = F,
         output_options=list(self_contained=FALSE,
                             lib_dir="html_site/site_libs", toc = TRUE,toc_float = TRUE, number_sections= TRUE))
}

```


# Code a simple one-variable regression
For the first coding exercise, you'll create a formula to define a one-variable modeling task, and then fit a linear model to the data. You are given the rates of male and female unemployment in the United States over several years (Source).

The task is to predict the rate of female unemployment from the observed rate of male unemployment. The outcome is female_unemployment, and the input is male_unemployment.

The sign of the variable coefficient tells you whether the outcome increases (+) or decreases (-) as the variable increases.

Recall the calling interface for lm() is:

lm(formula, data = ___)

```{r}
# unemployment is loaded in the workspace
summary(unemployment)

# Define a formula to express female_unemployment as a function of male_unemployment
fmla <- female_unemployment~male_unemployment

# Print it
fmla

# Use the formula to fit a model: unemployment_model
unemployment_model <- lm(fmla,unemployment)

# Print it
unemployment_model 

```


```{r}
# broom and sigr are already loaded in your workspace
# Print unemployment_model
unemployment_model

# Call summary() on unemployment_model to get more details
summary(unemployment_model)

# Call glance() on unemployment_model to see the details in a tidier form
glance(unemployment_model)

# Call wrapFTest() on unemployment_model to see the most relevant details
wrapFTest(unemployment_model)

```



```{r}

```



```{r}

```


```{r}

```


```{r}

```



```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
