---
title: "Regression with R"
---

```{r eval=FALSE, echo=FALSE}
pacman::p_load(rgeos,rgdal,learnr,skimr,ggvis,googleVis,corrplot,
               PerformanceAnalytics,rgdal,ggmap,rgeos,
               revealjs,DT,leaflet,data.table,
               leaflet.extras,caret,rpart,ggplot2,ipred,randomForest,
               rpart.plot,class,e1071,neuralnet,nnet,devtools,
               xgboost,AUC,hydroGOF,gbm,parallel,readr,RColorBrewer,gridExtra,
               rpart,psych,rmarkdown, rpart.plot,corrplot,DT,
               BBmisc,ParamHelpers,kernlab,ranger,irace,cmaes,
               GenSA,XML,mlr,MASS,arules,
               arulesViz,sjPlot,sjmisc,pROC,readxl,tidyverse,broom,staplr,Hmisc,
               tabplot,GGally,insuranceData,dummies,fastDummies,glmnet,plotly,dplyr
               ,DiagrammeR,Ckmeans.1d.dp,caret,lubridate, magrittr,knitr, ggpubr,countrycode,pROC,verification,countrycode,shinydashboard,shiny)
```

```{r echo=FALSE, eval=FALSE}

#####  chemin relatif du dossier contenant les fichiers ######
data.path="https://dataks.bitbucket.io/ml/"
data.path="C:/Users/SHIK/Documents/GitHub/dataks.bitbucket.io/ml/"
data.path="../../../DS/data/test/"

######### choix fichier #############

files=list.files(pattern = ".Rmd")
files.excluded = c("house_price_prediction.Rmd","regression_mlr.Rmd")
files = setdiff(files, files.excluded)

######### type fichier #############

type_document=c("html_document","html")
type_document=c("revealjs::revealjs_presentation","revealjs")
type_document=c("pdf_document","pdf")
type_document=c("beamer_presentation","beamer")

####### boucle de render  ############

for (file in files){
  render(file,"html_document",
         output_file = paste0(substr(file,1,(nchar(file)-4)),".html"),
         encoding="UTF-8",
         output_dir = "html_site",
         quiet = F,
         output_options=list(self_contained=FALSE,
                             lib_dir="html_site/site_libs", toc = TRUE,toc_float = TRUE, number_sections= TRUE))
}

```


# Code a simple one-variable regression
For the first coding exercise, you'll create a formula to define a one-variable modeling task, and then fit a linear model to the data. You are given the rates of male and female unemployment in the United States over several years (Source).

The task is to predict the rate of female unemployment from the observed rate of male unemployment. The outcome is female_unemployment, and the input is male_unemployment.

The sign of the variable coefficient tells you whether the outcome increases (+) or decreases (-) as the variable increases.

Recall the calling interface for lm() is:

lm(formula, data = ___)

```{r}
# unemployment is loaded in the workspace
summary(unemployment)

# Define a formula to express female_unemployment as a function of male_unemployment
fmla <- female_unemployment~male_unemployment

# Print it
fmla

# Use the formula to fit a model: unemployment_model
unemployment_model <- lm(fmla,unemployment)

# Print it
unemployment_model 

```


```{r}
# broom and sigr are already loaded in your workspace
# Print unemployment_model
unemployment_model

# Call summary() on unemployment_model to get more details
summary(unemployment_model)

# Call glance() on unemployment_model to see the details in a tidier form
glance(unemployment_model)

# Call wrapFTest() on unemployment_model to see the most relevant details
wrapFTest(unemployment_model)

```

# Predicting from the unemployment model

In this exercise, you will use your unemployment model unemployment_model to make predictions from the unemployment data, and compare predicted female unemployment rates to the actual observed female unemployment rates on the training data, unemployment. You will also use your model to predict on the new data in newrates, which consists of only one observation, where male unemployment is 5%.

The predict() interface for lm models takes the form

predict(model, newdata)
You will use the ggplot2 package to make the plots, so you will add the prediction column to the unemployment data frame. You will plot outcome versus prediction, and compare them to the line that represents perfect predictions (that is when the outcome is equal to the predicted value).

The ggplot2 command to plot a. 


```{r}
# unemployment is in your workspace
summary(unemployment)

# newrates is in your workspace
newrates

# Predict female unemployment in the unemployment data set
unemployment$prediction <-  predict(unemployment_model, unemployment)

# load the ggplot2 package
library(ggplot2)

# Make a plot to compare predictions to actual (prediction on x axis). 
ggplot(unemployment, aes(x = prediction, y =  female_unemployment)) + 
  geom_point() +
  geom_abline(color = "blue")

# Predict female unemployment rate when male unemployment is 5%
newMaleEmploment = data.frame(male_unemployment = 5 /100)

pred <- predict(unemployment_model, newrates )
# Print it
pred
```

# Multivariate linear regression (Part 1)

In this exercise, you will work with the blood pressure dataset (Source), and model blood_pressure as a function of weight and age.

```{r}

# bloodpressure is in your workspace
summary(bloodpressure)

# bloodpressure_model is in your workspace
bloodpressure_model

# predict blood pressure using bloodpressure_model :prediction
bloodpressure$prediction <-  predict(bloodpressure_model, bloodpressure)

# plot the results
ggplot(bloodpressure, aes(x = prediction, y = blood_pressure))+ 
  geom_point() +
    geom_abline(color = "blue")

```
# Advantages of lm

- Easy to fit and to apply
- Concise 
- Less prone to overfitting 
- Interpretable

# Cons 

- Can only epxress linear and additive relationships
- Colllinearity  


# Evaluation a model graphical


Gain curve, it 'is useful when  sorting the forecasting value is more importantn than predict the excat value.

# Graphically evaluate the unemployment model

In this exercise you will graphically evaluate the unemployment model, unemployment_model, that you fit to the unemployment data in the previous chapter. Recall that the model predicts female_unemployment from male_unemployment.

You will plot the model's predictions against the actual female_unemployment; recall the command is of the form

ggplot(dframe, aes(x = pred, y = outcome)) + 
       geom_point() +  
       geom_abline()
Then you will calculate the residuals:

residuals <- actual outcome - predicted outcome
and plot predictions against residuals. The residual graph will take a slightly different form: you compare the residuals to the horizontal line x=0 (using geom_hline()) rather than to the line x=y. The command will be provided.

The data frame unemployment and model unemployment_model are available in the workspace.

```{r}
# unemployment, unemployment_model are in the workspace
summary(unemployment)
summary(unemployment_model)

# Make predictions from the model
unemployment$predictions <- predict(unemployment_model)

# Fill in the blanks to plot predictions (on x-axis) versus the female_unemployment rates
ggplot(unemployment, aes(x = predictions, y = female_unemployment)) + 
  geom_point() + 
  geom_abline()
```


```{r}
# From previous step
unemployment$predictions <- predict(unemployment_model)

# Calculate residuals
unemployment$residuals <- resid(unemployment_model)

# Fill in the blanks to plot predictions (on x-axis) versus the residuals
ggplot(unemployment, aes(x = predictions, y = residuals)) + 
  geom_pointrange(aes(ymin = 0, ymax = residuals)) + 
  geom_hline(yintercept = 0, linetype = 3) + 
  ggtitle("residuals vs. linear model prediction")

```

# The gain curve to evaluate the unemployment model

In the previous exercise you made predictions about female_unemployment and visualized the predictions and the residuals. Now, you will also plot the gain curve of the unemployment_model's predictions against actual female_unemployment using the WVPlots::GainCurvePlot() function.

For situations where order is more important than exact values, the gain curve helps you check if the model's predictions sort in the same order as the true outcome.

Calls to the function GainCurvePlot() look like:

GainCurvePlot(frame, xvar, truthvar, title)
where

frame is a data frame
xvar and truthvar are strings naming the prediction and actual outcome columns of frame
title is the title of the plot
When the predictions sort in exactly the same order, the relative Gini coefficient is 1. When the model sorts poorly, the relative Gini coefficient is close to zero, or even negative.

```{r}

# unemployment is in the workspace (with predictions)
summary(unemployment)

# unemployment_model is in the workspace
summary(unemployment_model)

# Load the package WVPlots
library(WVPlots)

# Plot the Gain Curve
GainCurvePlot(unemployment,"predictions","female_unemployment","Unemployment model")

```

# RMSE 

Comparer le RMSE à l'écart type pour avoir une appréciation juste du modèle.

# Calculate RMSE

In this exercise you will calculate the RMSE of your unemployment model. In the previous coding exercises, you added two columns to the unemployment dataset:

the model's predictions (predictions column)
the residuals between the predictions and the outcome (residuals column)
You can calculate the RMSE from a vector of residuals, res, as:


You want RMSE to be small. How small is "small"? One heuristic is to compare the RMSE to the standard deviation of the outcome. With a good model, the RMSE should be smaller.
```{r}

# unemployment is in the workspace
summary(unemployment)

# For convenience put the residuals in the variable res
res <- unemployment$residuals

# Calculate RMSE, assign it to the variable rmse and print it
(rmse <- sqrt(mean(res^2)))

# Calculate the standard deviation of female_unemployment and print it
(sd_unemployment <- sd(unemployment$female_unemployment))


```


Calculate R-Squared
Now that you've calculated the RMSE of your model's predictions, you will examine how well the model fits the data: that is, how much variance does it explain. You can do this using R2.

Suppose y is the true outcome, p is the prediction from the model, and res=y−p are the residuals of the predictions.

Then the total sum of squares tss ("total variance") of the data is:

tss=∑(y−y¯¯¯)2
where y¯¯¯ is the mean value of y.

The residual sum of squared errors of the model, rss is:
rss=∑res2
R2 (R-Squared), the "variance explained" by the model, is then:

1−rsstss
After you calculate R2, you will compare what you computed with the R2 reported by glance(). glance() returns a one-row data frame; for a linear regression model, one of the columns returned is the R2 of the model on the training data.

The data frame unemployment is in your workspace, with the columns predictions and residuals that you calculated in a previous exercise.


```{r}
# unemployment is in your workspace
summary(unemployment)

# unemployment_model is in the workspace
summary(unemployment_model)

# Calculate mean female_unemployment: fe_mean. Print it
(fe_mean <- mean(unemployment$female_unemployment))

# Calculate total sum of squares: tss. Print it
(tss <- sum((unemployment$female_unemployment - fe_mean)^2))

# Calculate residual sum of squares: rss. Print it
(rss <- sum(unemployment$residuals^2))

# Calculate R-squared: rsq. Print it. Is it a good fit?
(rsq <- 1-rss/tss)


```

# Correlation and R-squared

The linear correlation of two variables, x and y, measures the strength of the linear relationship between them. When x and y are respectively:

the outcomes of a regression model that minimizes squared-error (like linear regression) and
the true outcomes of the training data,
then the square of the correlation is the same as R2. You will verify that in this exercise.

```{r}
# unemployment is in your workspace
summary(unemployment)

# unemployment_model is in the workspace
summary(unemployment_model)

# Get the correlation between the prediction and true outcome: rho and print it
(rho <- cor(unemployment$female_unemployment, unemployment$predictions))

# Square rho: rho2 and print it
(rho2 <- rho^2)

# Get R-squared from glance and print it
(rsq_glance <- glance(unemployment_model)$r.squared)

```


# Cross Validation


Recommandation 

La cross validation doit être utilisé quand nous ne disposons pas d'assez de données.


```{r}
# mpg is in the workspace
summary(mpg)
dim(mpg)

# Use nrow to get the number of rows in mpg (N) and print it
(N <- nrow(mpg))

# Calculate how many rows 75% of N should be and print it
# Hint: use round() to get an integer
(target <- round(N*0.75))
# Create the vector of N uniform random variables: gp
gp <- runif(N)

# Use gp to create the training set: mpg_train (75% of data) and mpg_test (25% of data)
x  = 0.75
mpg_train <- mpg[gp < x,]
mpg_test <-  mpg[gp >= x, ]


```

```{r}
# mpg_train is in the workspace
summary(mpg_train)

# Create a formula to express cty as a function of hwy: fmla and print it.
(fmla <- cty ~hwy)

# Now use lm() to build a model mpg_model from mpg_train that predicts cty from hwy 
mpg_model <- lm(fmla, mpg_train)

# Use summary() to examine the model
summary(mpg_model)
```


# Evaluate a model using test/train split

Now you will test the model mpg_model on the test data, mpg_test. Functions rmse() and r_squared() to calculate RMSE and R-squared have been provided for convenience:

rmse(predcol, ycol)
r_squared(predcol, ycol)
where:

predcol: The predicted values
ycol: The actual outcome
You will also plot the predictions vs. the outcome.

Generally, model performance is better on the training data than the test data (though sometimes the test set "gets lucky"). A slight difference in performance is okay; if the performance on training is significantly better, there is a problem.

```{r}
# Examine the objects in the workspace
ls.str()

# predict cty from hwy for the training set
(mpg_train$pred <- predict(mpg_model ,mpg_train))

# predict cty from hwy for the test set
(mpg_test$pred <-predict( mpg_model, mpg_test))

# Evaluate the rmse on both training and test data and print them
(rmse_train <- rmse(mpg_train$pred, mpg_train$cty ) )
(rmse_test <- rmse(mpg_test$pred, mpg_test$cty ))

# Evaluate the r-squared on both training and test data.and print them
(rsq_train <- r_squared(mpg_train$pred, mpg_train$cty ))
(rsq_test <- r_squared(mpg_test$pred, mpg_test$cty))

# Plot the predictions (on the x-axis) against the outcome (cty) on the test data
ggplot(mpg_test, aes(x = pred, y = cty)) + 
  geom_point() + 
  geom_abline()

```


# Create a cross validation plan

There are several ways to implement an n-fold cross validation plan. In this exercise you will create such a plan using vtreat::kWayCrossValidation(), and examine it.

kWayCrossValidation() creates a cross validation plan with the following call:

splitPlan <- kWayCrossValidation(nRows, nSplits, dframe, y)
where nRows is the number of rows of data to be split, and nSplits is the desired number of cross-validation folds.

Strictly speaking, dframe and y aren't used by kWayCrossValidation; they are there for compatibility with other vtreat data partitioning functions. You can set them both to NULL.

The resulting splitPlan is a list of nSplits elements; each element contains two vectors:

train: the indices of dframe that will form the training set
app: the indices of dframe that will form the test (or application) set
In this exercise you will create a 3-fold cross-validation plan for the data set mpg

```{r}

# Load the package vtreat
library(vtreat)

# mpg is in the workspace
summary(mpg)

# Get the number of rows in mpg
nRows <- nrow(mpg)
# Implement the 3-fold cross-fold plan with vtreat
splitPlan <- kWayCrossValidation(nRows,3,NULL, NULL)

# Examine the split plan
str(splitPlan)
```


valuate a modeling procedure using n-fold cross-validation
In this exercise you will use splitPlan, the 3-fold cross validation plan from the previous exercise, to make predictions from a model that predicts mpg$cty from mpg$hwy.

If dframe is the training data, then one way to add a column of cross-validation predictions to the frame is as follows:

# Initialize a column of the appropriate length
dframe$pred.cv <- 0 

# k is the number of folds
# splitPlan is the cross validation plan

for(i in 1:k) {
  # Get the ith split
  split <- splitPlan[[i]]

  # Build a model on the training data 
  # from this split 
  # (lm, in this case)
  model <- lm(fmla, data = dframe[split$train,])

  # make predictions on the 
  # application data from this split
  dframe$pred.cv[split$app] <- predict(model, newdata = dframe[split$app,])
}
Cross-validation predicts how well a model built from all the data will perform on new data. As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close.

```{r}

# mpg is in the workspace
summary(mpg)

# splitPlan is in the workspace
str(splitPlan)

# Run the 3-fold cross validation plan from splitPlan
k <-3 # Number of folds
mpg$pred.cv <- 0 
for(i in 1:k) {
  split <- splitPlan[[i]]
  model <- lm(cty ~ hwy, data = mpg[split$train, ])
  mpg$pred.cv[split$app] <- predict(model, newdata = mpg[split$app,])
}

# Predict from a full model
mpg$pred <- predict(lm(cty ~ hwy, data = mpg),mpg)

```

Convert a categorical variable in numerical variable is often calls on hot encoded.



# Examining the structure of categorical inputs

For this exercise you will call model.matrix() to examine how R represents data with both categorical and numerical inputs for modeling. The dataset flowers (derived from the Sleuth3 package) is loaded into your workspace. It has the following columns:

Flowers: the average number of flowers on a meadowfoam plant
Intensity: the intensity of a light treatment applied to the plant
Time: A categorical variable - when (Late or Early) in the lifecycle the light treatment occurred
The ultimate goal is to predict Flowers as a function of Time and Intensity.

dataset **flower** 

```{r}

# Call str on flowers to see the types of each column

str(flowers)
# Use unique() to see how many possible values Time takes

unique(flowers$Time)

# Build a formula to express Flowers as a function of Intensity and Time: fmla. Print it
(fmla <- as.formula("Flowers ~ Intensity + Time"))

# Use fmla and model.matrix to see how the data is represented for modeling
mmat <- model.matrix(fmla, flowers)

# Examine the first 20 lines of flowers

head(flowers,20)
# Examine the first 20 lines of mmat
head(mmat,20)
```

# Modeling with categorical inputs

For this exercise you will fit a linear model to the flowers data, to predict Flowers as a function of Time and Intensity.

The model formula fmla that you created in the previous exercise is still in your workspace, as is the model matrix mmat.

```{r}
# flowers in is the workspace
str(flowers)

# fmla is in the workspace
fmla

# Fit a model to predict Flowers from Intensity and Time : flower_model
flower_model <- lm(fmla, data = flowers)

# Use summary on mmat to remind yourself of its structure

summary(mmat)
# Use summary to examine flower_model 
summary(flower_model)

# Predict the number of flowers on each plant
flowers$predictions <- predict(flower_model)

# Plot predictions vs actual flowers (predictions on x-axis)
ggplot(flowers, aes(x = predictions, y = Flowers)) + 
  geom_point() +
  geom_abline(color = "blue") 

```


# Modeling an interaction

In this exercise you will use interactions to model the effect of gender and gastric activity on alcohol metabolism.

The data frame alcohol has columns:

Metabol: the alcohol metabolism rate
Gastric: the rate of gastric alcohol dehydrogenase activity
Sex: the sex of the drinker (Male or Female)
In the video, we fit three models to the alcohol data:

one with only additive (main effect) terms : Metabol ~ Gastric + Sex
two models, each with interactions between gastric activity and sex
We saw that one of the models with interaction terms had a better R-squared than the additive model, suggesting that using interaction terms gives a better fit. In this exercise we will compare the R-squared of one of the interaction models to the main-effects-only model.

Recall that the operator : designates the interaction between two variables. The operator * designates the interaction between the two variables, plus the main effects.

```{r}
# alcohol is in the workspace
summary(alcohol)

# Create the formula with main effects only
(fmla_add <- as.formula(Metabol~Gastric+Sex) )

# Create the formula with interactions
(fmla_interaction <- Metabol~Gastric+Gastric:Sex)

# Fit the main effects only model
model_add <- lm(fmla_add, data = alcohol)

# Fit the interaction model
model_interaction <- lm(fmla_interaction, data = alcohol)

# Call summary on both models and compare

summary(model_add)
summary(model_interaction)

```

# Modeling an interaction (2)

In this exercise, you will compare the performance of the interaction model you fit in the previous exercise to the performance of a main-effects only model. Because this data set is small, we will use cross-validation to simulate making predictions on out-of-sample data.

You will begin to use the dplyr package to do calculations.

mutate() adds new columns to a tbl (a type of data frame)
group_by() specifies how rows are grouped in a tbl
summarize() computes summary statistics of a column
You will also use tidyr's gather() which takes multiple columns and collapses them into key-value pairs.


```{r}
# alcohol is in the workspace
summary(alcohol)

# Both the formulae are in the workspace
fmla_add
fmla_interaction
# number of kfold 
k = 3
# Create the splitting plan for 3-fold cross validation
set.seed(34245)  # set the seed for reproducibility
splitPlan <- kWayCrossValidation(nrow(alcohol),k , NULL, NULL)

# Sample code: Get cross-val predictions for main-effects only model
alcohol$pred_add <- 0  # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_add <- lm(fmla_add, data = alcohol[split$train, ])
  alcohol$pred_add[split$app] <- predict(model_add, newdata = alcohol[split$app, ])
}

# Get the cross-val predictions for the model with interactions
alcohol$pred_interaction <- 0 # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_interaction <- lm(fmla_interaction, data = alcohol[split$train, ])
  alcohol$pred_interaction[split$app] <- predict(model_interaction, newdata = alcohol[split$app, ])
}

# Get RMSE
alcohol %>% 
  gather(key = modeltype, value = pred, pred_add, pred_interaction) %>%
  mutate(residuals = Metabol -pred) %>%      
  group_by(modeltype) %>%
  summarize(rmse = sqrt(mean(residuals^2)))

```

# Relative error

In this exercise, you will compare relative error to absolute error. For the purposes of modeling, we will define relative error as

rel=(pred−y)y
that is, the error is relative to the true outcome. You will measure the overall relative error of a model using root mean squared relative error:

rmserel=(√rel2¯¯¯¯¯¯¯¯)
where rel2¯¯¯¯¯¯¯¯ is the mean of rel2.

The example (toy) dataset fdata is loaded in your workspace. It includes the columns:

y: the true output to be predicted by some model; imagine it is the amount of money a customer will spend on a visit to your store.
pred: the predictions of a model that predicts y.
label: categorical: whether y comes from a population that makes small purchases, or large ones.
You want to know which model does "better": the one predicting the small purchases, or the one predicting large ones.

```{r}
# fdata is in the workspace
summary(fdata)

# Examine the data: generate the summaries for the groups large and small:
fdata %>% 
    group_by(label) %>%     # group by small/large purchases
    summarize(min  = min(y),   # min of y
              mean = mean(y),   # mean of y
              max  = max(y))   # max of y

# Fill in the blanks to add error columns
fdata2 <- fdata %>% 
         group_by(label) %>%       # group by label
           mutate(residual = pred-y,  # Residual
                  relerr   =  residual/ y)  # Relative error

# Compare the rmse and rmse.rel of the large and small groups:
fdata2 %>% 
  group_by(label) %>% 
  summarize(rmse     = sqrt(mean(residual^2)),   # RMSE
            rmse.rel = sqrt(mean(relerr^2)))   # Root mean squared relative error
            
# Plot the predictions for both groups of purchases
ggplot(fdata2, aes(x = pred, y = y, color = label)) + 
  geom_point() + 
  geom_abline() + 
  facet_wrap(~ label, ncol = 1, scales = "free") + 
  ggtitle("Outcome vs prediction")

```

# Modeling log-transformed monetary output

In this exercise, you will practice modeling on log-transformed monetary output, and then transforming the "log-money" predictions back into monetary units. The data loaded into your workspace records subjects' incomes in 2005 (Income2005), as well as the results of several aptitude tests taken by the subjects in 1981:

Arith
Word
Parag
Math
AFQT (Percentile on the Armed Forces Qualifying Test)
The data have already been split into training and test sets (income_train and income_test respectively) and are in the workspace. You will build a model of log(income) from the inputs, and then convert log(income) back into income.

```{r}
# Examine Income2005 in the training set
summary(income_train$Income2005)

# Write the formula for log income as a function of the tests and print it
(fmla.log <- as.formula(log(Income2005)~ Arith+Word+Parag+Math+AFQT))

# Fit the linear model
model.log <-  lm(fmla.log,data = income_train)

# Make predictions on income_test
income_test$logpred <- predict(model.log, income_test)
summary(income_test$logpred)

# Convert the predictions to monetary units
income_test$pred.income <- exp(income_test$logpred)
summary(income_test$pred.income)

#  Plot predicted income (x axis) vs income
ggplot(income_test, aes(x = pred.income, y = Income2005)) + 
  geom_point() + 
  geom_abline(color = "blue")

```

# Comparing RMSE and root-mean-squared Relative Error

In this exercise, you will show that log-transforming a monetary output before modeling improves mean relative error (but increases RMSE) compared to modeling the monetary output directly. You will compare the results of model.log from the previous exercise to a model (model.abs) that directly fits income.

The income_train and income_test datasets are loaded in your workspace, along with your model, model.log.

Also in the workspace:

model.abs: a model that directly fits income to the inputs using the formula

Income2005 ~ Arith + Word + Parag + Math + AFQT

```{r}
# fmla.abs is in the workspace
fmla.abs

# model.abs is in the workspace
summary(model.abs)

# Add predictions to the test set
income_test <- income_test %>%
  mutate(pred.absmodel = predict(model.abs, income_test),      # predictions from model.abs
         pred.logmodel = exp(predict(model.log, income_test))) # predictions from model.log

# Gather the predictions and calculate residuals and relative error
income_long <- income_test %>% 
  gather(key = modeltype, value = pred, pred.absmodel, pred.logmodel) %>%
  mutate(residual = pred - Income2005,     # residuals
         relerr   = residual / Income2005) # relative error

# Calculate RMSE and relative RMSE and compare
income_long %>% 
  group_by(modeltype) %>%                       # group by modeltype
  summarize(rmse     = sqrt(mean(residual^2)),  # RMSE
            rmse.rel = sqrt(mean(relerr^2)))    # Root mean squared relative error

```

# Input transforms: the "hockey stick"

In this exercise, we will build a model to predict price from a measure of the house's size (surface area). The data set houseprice has the columns:

price : house price in units of $1000
size: surface area
A scatterplot of the data shows that the data is quite non-linear: a sort of "hockey-stick" where price is fairly flat for smaller houses, but rises steeply as the house gets larger. Quadratics and tritics are often good functional forms to express hockey-stick like relationships. Note that there may not be a "physical" reason that price is related to the square of the size; a quadratic is simply a closed form approximation of the observed relationship.

scatterplot

You will fit a model to predict price as a function of the squared size, and look at its fit on the training data.

Because ^ is also a symbol to express interactions, use the function I() to treat the expression x^2 “as is”: that is, as the square of x rather than the interaction of x with itself.

exampleFormula = y ~ I(x^2)

dataset **houseprice**

```{r}
# houseprice is in the workspace
summary(houseprice)

# Create the formula for price as a function of squared size
(fmla_sqr <- as.formula(price~ I(size^2)))

# Fit a model of price as a function of squared size (use fmla_sqr)
model_sqr <- lm(fmla_sqr, houseprice)
# Fit a model of price as a linear function of size
model_lin <- lm(price~size,houseprice)

# Make predictions and compare
houseprice %>% 
    mutate(pred_lin = predict(model_lin),       # predictions from linear model
           pred_sqr = predict(model_sqr)) %>%   # predictions from quadratic model 
    gather(key = modeltype, value = pred, pred_lin, pred_sqr) %>% # gather the predictions
    ggplot(aes(x = size)) + 
       geom_point(aes(y = price)) +                   # actual prices
       geom_line(aes(y =pred, color = modeltype)) + # the predictions
       scale_color_brewer(palette = "Dark2")
```

```{r}
# houseprice is in the workspace
summary(houseprice)

# fmla_sqr is in the workspace
fmla_sqr

# Create a splitting plan for 3-fold cross validation
set.seed(34245)  # set the seed for reproducibility
k = 3
splitPlan <- kWayCrossValidation(nrow(houseprice),k , NULL, NULL)

# Sample code: get cross-val predictions for price ~ size
houseprice$pred_lin <- 0  # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_lin <- lm(price ~ size, data = houseprice[split$train,])
  houseprice$pred_lin[split$app] <- predict(model_lin, newdata = houseprice[split$app,])
}

# Get cross-val predictions for price as a function of size^2 (use fmla_sqr)
houseprice$pred_sqr <- 0 # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_sqr <- lm(fmla_sqr, data = houseprice[split$train, ])
  houseprice$pred_sqr[split$app] <- predict(model_sqr, newdata = houseprice[split$app, ])
}

# Gather the predictions and calculate the residuals
houseprice_long <- houseprice %>%
  gather(key = modeltype, value = pred, pred_lin, pred_sqr) %>%
  mutate(residuals = pred - price)

# Compare the cross-validated RMSE for the two models
houseprice_long %>% 
  group_by(modeltype) %>% # group by modeltype
  summarize(rmse =  sqrt(mean(residuals^2)))
```

# Fit a model of sparrow survival probability

In this exercise, you will estimate the probability that a sparrow survives a severe winter storm, based on physical characteristics of the sparrow. The dataset sparrow is loaded into your workspace. The outcome to be predicted is status ("Survived", "Perished"). The variables we will consider are:

total_length: length of the bird from tip of beak to tip of tail (mm)
weight: in grams
humerus : length of humerus ("upper arm bone" that connects the wing to the body) (inches)
Remember that when using glm() to create a logistic regression model, you must explicitly specify that family = binomial:

glm(formula, data = data, family = binomial)
You will call summary(), broom::glance() to see different functions for examining a logistic regression model. One of the diagnostics that you will look at is the analog to R2, called pseudo-R2.

pseudoR2=1−deviancenull.deviance
You can think of deviance as analogous to variance: it is a measure of the variation in categorical data. The pseudo-R2 is analogous to R2 for standard regression: R2 is a measure of the "variance explained" of a regression model. The pseudo-R2 is a measure of the "deviance explained".

```{r}
# sparrow is in the workspace
summary(sparrow)

# Create the survived column
sparrow$survived <- sparrow$status == "Survived"

# Create the formula
(fmla <- survived~total_length+weight+humerus)

# Fit the logistic regression model
sparrow_model <- glm(fmla, data = sparrow, family = binomial)

# Call summary
summary(sparrow_model)

# Call glance
(perf <- glance(sparrow_model))

# Calculate pseudo-R-squared
(pseudoR2 <- 1 - perf$deviance/perf$null.deviance)

```


# Predict sparrow survival
In this exercise you will predict the probability of survival using the sparrow survival model from the previous exercise.

Recall that when calling predict() to get the predicted probabilities from a glm() model, you must specify that you want the response:

predict(model, type = "response")
Otherwise, predict() on a logistic regression model returns the predicted log-odds of the event, not the probability.

You will also use the GainCurvePlot() function to plot the gain curve from the model predictions. If the model's gain curve is close to the ideal ("wizard") gain curve, then the model sorted the sparrows well: that is, the model predicted that sparrows that actually survived would have a higher probability of survival. The inputs to the GainCurvePlot() function are:

frame: data frame with prediction column and ground truth column
xvar: the name of the column of predictions (as a string)
truthVar: the name of the column with actual outcome (as a string)
title: a title for the plot (as a string)
GainCurvePlot(frame, xvar, truthVar, title)

```{r}
# sparrow is in the workspace
summary(sparrow)

# sparrow_model is in the workspace
summary(sparrow_model)

# Make predictions
sparrow$pred <- predict(sparrow_model, type = "response")
# Look at gain curve
GainCurvePlot(sparrow,'pred','survived', "sparrow survival model")

```


# Fit a model to predict bike rental counts

In this exercise you will build a model to predict the number of bikes rented in an hour as a function of the weather, the type of day (holiday, working day, or weekend), and the time of day. You will train the model on data from the month of July.

The data frame has the columns:

cnt: the number of bikes rented in that hour (the outcome)
hr: the hour of the day (0-23, as a factor)
holiday: TRUE/FALSE
workingday: TRUE if neither a holiday nor a weekend, else FALSE
weathersit: categorical, "Clear to partly cloudy"/"Light Precipitation"/"Misty"
temp: normalized temperature in Celsius
atemp: normalized "feeling" temperature in Celsius
hum: normalized humidity
windspeed: normalized windspeed
instant: the time index -- number of hours since beginning of data set (not a variable)
mnth and yr: month and year indices (not variables)
Remember that you must specify family = poisson or family = quasipoisson when using glm() to fit a count model.

Since there are a lot of input variables, for convenience we will specify the outcome and the inputs in variables, and use paste() to assemble a string representing the model formula.

** Remarque**

utliser la regression poisson quand mean = varaiance 
autrement utiliser la qpoisson distribution


```{r}
# bikesJuly is in the workspace
str(bikesJuly)

# The outcome column
outcome 

# The inputs to use
vars 

# Create the formula string for bikes rented as a function of the inputs
(fmla <- paste(outcome, "~", paste(vars, collapse = " + ")))

# Calculate the mean and variance of the outcome
(mean_bikes <- mean(bikesJuly$cnt))
(var_bikes <- var(bikesJuly$cnt))

# Fit the model
bike_model <- glm(fmla,data = bikesJuly,family = quasipoisson)

# Call glance
(perf <- glance(bike_model))

# Calculate pseudo-R-squared
(pseudoR2 <-  1- perf$deviance/perf$null.deviance)
```

# Predict bike rentals on new data

In this exercise you will use the model you built in the previous exercise to make predictions for the month of August. The data set bikesAugust has the same columns as bikesJuly.

Recall that you must specify type = "response" with predict() when predicting counts from a glm poisson or quasipoisson model.

```{r}

# bikesAugust is in the workspace
str(bikesAugust)

# bike_model is in the workspace
summary(bike_model)

# Make predictions on August data
bikesAugust$pred  <- predict(bike_model, newdata = bikesAugust, type = 'response')

# Calculate the RMSE
bikesAugust %>% 
  mutate(residual = pred - bikesAugust$cnt) %>%
  summarize(rmse  =  sqrt(mean(residual^2)))

# Plot predictions vs cnt (pred on x-axis)
ggplot(bikesAugust, aes(x = pred, y = cnt)) +
  geom_point() + 
  geom_abline(color = "darkblue")

```

Visualize the Bike Rental Predictions
In the previous exercise, you visualized the bike model's predictions using the standard "outcome vs. prediction" scatter plot. Since the bike rental data is time series data, you might be interested in how the model performs as a function of time. In this exercise, you will compare the predictions and actual rentals on an hourly basis, for the first 14 days of August.

To create the plot you will use the function tidyr::gather() to consolidate the predicted and actual values from bikesAugust in a single column. gather() takes as arguments:

The "wide" data frame to be gathered (implicit in a pipe)
The name of the key column to be created - contains the names of the gathered columns.
The name of the value column to be created - contains the values of the gathered columns.
The names of the columns to be gathered into a single column.
You'll use the gathered data frame to compare the actual and predicted rental counts as a function of time. The time index, instant counts the number of observations since the beginning of data collection. The sample code converts the instants to daily units, starting from 0.

```{r}

# Plot predictions and cnt by date/time
bikesAugust %>% 
  # set start to 0, convert unit to days
  mutate(instant = (instant - min(instant))/24) %>%  
  # gather cnt and pred into a value column
  gather(key = valuetype, value = value, cnt, pred) %>%
  filter(instant < 14) %>% # restrict to first 14 days
  # plot value by instant
  ggplot(aes(x = instant, y = value, color = valuetype, linetype = valuetype)) + 
  geom_point() + 
  geom_line() + 
  scale_x_continuous("Day", breaks = 0:14, labels = 0:14) + 
  scale_color_brewer(palette = "Dark2") + 
  ggtitle("Predicted August bike rentals, Quasipoisson model")

```

# Writing formulas for GAM models

When using gam() to model outcome as an additive function of the inputs, you can use the s() function inside formulas to designate that you want use a spline to model the non-linear relationship of a continuous variable to the outcome.

Suppose that you want to predict how much weight (Wtloss) a dieter will lose over a 2-year diet plan as a function of:

Diet type (categorical)
Sex (categorical)
Age at beginning of diet (continuous)
BMI (body mass index) at beginning of diet (continuous)
You do not want to assume that any of the relationships are linear.

Which is the most appropriate formula?

**Remarque**

Il ne faut utiliser GAM que si  on est face un modèle non linéaire dont on ne connait pas la relation à priori ( aucune connaissance métier).


Model soybean growth with GAM
In this exercise you will model the average leaf weight on a soybean plant as a function of time (after planting). As you will see, the soybean plant doesn't grow at a steady rate, but rather has a "growth spurt" that eventually tapers off. Hence, leaf weight is not well described by a linear model.

Recall that you can designate which variable you want to model non-linearly in a formula with the s() function:

y ~ s(x)
Also remember that gam() from the package mgcv has the calling interface

gam(formula, family, data)
For standard regression, use family = gaussian (the default).

The soybean training data, soybean_train is loaded into your workspace. It has two columns: the outcome weight and the variable Time. For comparison, the linear model model.lin, which was fit using the formula weight ~ Time has already been loaded into the workspace as well.

```{r}
# soybean_train is in the workspace
summary(soybean_train)

# Plot weight vs Time (Time on x axis)
ggplot(soybean_train, aes(x = Time , y = weight)) + 
  geom_point() 
```

```{r}
# From previous step
library(mgcv)
fmla.gam <- weight ~ s(Time)
model.gam <- gam(fmla.gam, data = soybean_train, family = gaussian)

# Call summary() on model.lin and look for R-squared
summary(model.lin)
# Call summary() on model.gam and look for R-squared
summary(model.gam)

# Call plot() on model.gam

plot(model.gam)
```

# Predict with the soybean model on test data

In this exercise you will apply the soybean models from the previous exercise (model.lin and model.gam, already in your workspace) to new data: soybean_test.

```{r}
# soybean_test is in the workspace
summary(soybean_test)

# Get predictions from linear model
soybean_test$pred.lin <- predict(model.lin, newdata = soybean_test)

# Get predictions from gam model
soybean_test$pred.gam <- as.numeric(predict(model.gam, newdata = soybean_test))

# Gather the predictions into a "long" dataset
soybean_long <- soybean_test %>%
  gather(key = modeltype, value = pred, pred.lin, pred.gam)

# Calculate the rmse
soybean_long %>%
  mutate(residual = weight - pred) %>%     # residuals
  group_by(modeltype) %>%                  # group by modeltype
  summarize(rmse = sqrt(mean(residual^2))) # calculate the RMSE

# Compare the predictions against actual weights on the test data
soybean_long %>%
  ggplot(aes(x = Time)) +                          # the column for the x axis
  geom_point(aes(y = weight)) +                    # the y-column for the scatterplot
  geom_point(aes(y = pred, color = modeltype)) +   # the y-column for the point-and-line plot
  geom_line(aes(y = pred, color = modeltype, linetype = modeltype)) + # the y-column for the point-and-line plot
  scale_color_brewer(palette = "Dark2")

```

# Build a random forest model for bike rentals

In this exercise you will again build a model to predict the number of bikes rented in an hour as a function of the weather, the type of day (holiday, working day, or weekend), and the time of day. You will train the model on data from the month of July.

You will use the ranger package to fit the random forest model. For this exercise, the key arguments to the ranger() call are:

formula
data
num.trees: the number of trees in the forest.
respect.unordered.factors : Specifies how to treat unordered factor variables. We recommend setting this to "order" for regression.
seed: because this is a random algorithm, you will set the seed to get reproducible results
Since there are a lot of input variables, for convenience we will specify the outcome and the inputs in the variables outcome and vars, and use paste() to assemble a string representing the model formula.

```{r}
# bikesJuly is in the workspace
str(bikesJuly)

# Random seed to reproduce results
seed

# the outcome column
(outcome <- "cnt")

# The input variables
(vars <- c("hr", "holiday", "workingday", "weathersit", "temp", "atemp", "hum", "windspeed"))

# Create the formula string for bikes rented as a function of the inputs
(fmla <- paste(outcome, "~", paste(vars, collapse = " + ")))

# Load the package ranger
library(ranger)

# Fit and print the random forest model.
(bike_model_rf <- ranger(fmla, 
                         bikesJuly, 
                         num.trees = 500, 
                         respect.unordered.factors = "order", 
                         seed = seed))

```

# Predict bike rentals with the random forest model

In this exercise you will use the model that you fit in the previous exercise to predict bike rentals for the month of August.

The predict() function for a ranger model produces a list. One of the elements of this list is predictions, a vector of predicted values. You can access predictions with the $ notation for accessing named elements of a list:




```{r}
# bikesAugust is in the workspace
str(bikesAugust)

# bike_model_rf is in the workspace
bike_model_rf

# Make predictions on the August data
bikesAugust$pred <- predict(bike_model_rf, bikesAugust)$predictions

# Calculate the RMSE of the predictions
bikesAugust %>% 
  mutate(residual = cnt - pred)  %>% # calculate the residual
  summarize(rmse  = sqrt(mean(residual^2)))      # calculate rmse

# Plot actual outcome vs predictions (predictions on x-axis)
ggplot(bikesAugust, aes(x = pred, y = cnt)) + 
  geom_point() + 
  geom_abline()

```

# Visualize random forest bike model predictions

In the previous exercise, you saw that the random forest bike model did better on the August data than the quasiposson model, in terms of RMSE.

In this exercise you will visualize the random forest model's August predictions as a function of time. The corresponding plot from the quasipoisson model that you built in a previous exercise is in the workspace for you to compare.

Recall that the quasipoisson model mostly identified the pattern of slow and busy hours in the day, but it somewhat underestimated peak demands. You would like to see how the random forest model compares.

The data frame bikesAugust (with predictions) is in the workspace. The plot quasipoisson_plot of quasipoisson model predictions as a function of time is shown.

```{r}

first_two_weeks <- bikesAugust %>% 
  # Set start to 0, convert unit to days
  mutate(instant = (instant - min(instant)) / 24) %>% 
  # Gather cnt and pred into a column named value with key valuetype
  gather(key = valuetype, value = value, cnt, pred) %>%
  # Filter for rows in the first two
  filter(instant < 14) 

# Plot predictions and cnt by date/time 
ggplot(first_two_weeks, aes(x = instant, y = value, color = valuetype, linetype = valuetype)) + 
  geom_point() + 
  geom_line() + 
  scale_x_continuous("Day", breaks = 0:14, labels = 0:14) + 
  scale_color_brewer(palette = "Dark2") + 
  ggtitle("Predicted August bike rentals, Random Forest plot")
```

```{r}

vtreat on a small example
In this exercise you will use vtreat to one-hot-encode a categorical variable on a small example. vtreat creates a treatment plan to transform categorical variables into indicator variables (coded "lev"), and to clean bad values out of numerical variables (coded "clean").

To design a treatment plan use the function designTreatmentsZ()

treatplan <- designTreatmentsZ(data, varlist)
data: the original training data frame
varlist: a vector of input variables to be treated (as strings).
designTreatmentsZ() returns a list with an element scoreFrame: a data frame that includes the names and types of the new variables:

scoreFrame <- treatplan %>% 
            magrittr::use_series(scoreFrame) %>% 
            select(varName, origName, code)
varName: the name of the new treated variable
origName: the name of the original variable that the treated variable comes from
code: the type of the new variable.
"clean": a numerical variable with no NAs or NaNs
"lev": an indicator variable for a specific level of the original categorical variable.
(magrittr::use_series() is an alias for $ that you can use in pipes.)

For these exercises, we want varName where code is either "clean" or "lev":

newvarlist <- scoreFrame %>% 
             filter(code %in% c("clean", "lev") %>%
             magrittr::use_series(varName)
To transform the data set into all numerical and one-hot-encoded variables, use prepare():

data.treat <- prepare(treatplan, data, varRestrictions = newvarlist)
treatplan: the treatment plan
data: the data frame to be treated
varRestrictions: the variables desired in the treated data
```


vtreat on a small example
In this exercise you will use vtreat to one-hot-encode a categorical variable on a small example. vtreat creates a treatment plan to transform categorical variables into indicator variables (coded "lev"), and to clean bad values out of numerical variables (coded "clean").

To design a treatment plan use the function designTreatmentsZ()

treatplan <- designTreatmentsZ(data, varlist)
data: the original training data frame
varlist: a vector of input variables to be treated (as strings).
designTreatmentsZ() returns a list with an element scoreFrame: a data frame that includes the names and types of the new variables:

scoreFrame <- treatplan %>% 
            magrittr::use_series(scoreFrame) %>% 
            select(varName, origName, code)
varName: the name of the new treated variable
origName: the name of the original variable that the treated variable comes from
code: the type of the new variable.
"clean": a numerical variable with no NAs or NaNs
"lev": an indicator variable for a specific level of the original categorical variable.
(magrittr::use_series() is an alias for $ that you can use in pipes.)

For these exercises, we want varName where code is either "clean" or "lev":

newvarlist <- scoreFrame %>% 
             filter(code %in% c("clean", "lev") %>%
             magrittr::use_series(varName)
To transform the data set into all numerical and one-hot-encoded variables, use prepare():

data.treat <- prepare(treatplan, data, varRestrictions = newvarlist)
treatplan: the treatment plan
data: the data frame to be treated
varRestrictions: the variables desired in the treated data

```{r}
# dframe is in the workspace
dframe = data
# Create and print a vector of variable names
(vars <- c("color","size"))
# Load the package vtreat
library(vtreat)
# Create the treatment plan
treatplan <- designTreatmentsZ(dframe,vars)

# Examine the scoreFrame
(scoreFrame <- treatplan %>%
    use_series(scoreFrame) %>%
    select(varName, origName, code))

# We only want the rows with codes "clean" or "lev"
(newvars <- scoreFrame %>%
    filter(code %in% c("clean","lev")) %>%
    use_series(varName))

# Create the treated training data
(dframe.treat <- prepare(treatplan, dframe, varRestriction = newvars))

```


# Novel levels

When a level of a categorical variable is rare, sometimes it will fail to show up in training data. If that rare level then appears in future data, downstream models may not know what to do with it. When such novel levels appear, using model.matrix or caret::dummyVars to one-hot-encode will not work correctly.

vtreat is a "safer" alternative to model.matrix for one-hot-encoding, because it can manage novel levels safely. vtreat also manages missing values in the data (both categorical and continuous).

In this exercise you will see how vtreat handles categorical values that did not appear in the training set. The treatment plan treatplan and the set of variables newvars from the previous exercise are still in your workspace. dframe and a new data frame testframe are also in your workspace.

```{r}
# treatplan is in the workspace
summary(treatplan)

# newvars is in the workspace
newvars

# Print dframe and testframe
dframe
testframe

# Use prepare() to one-hot-encode testframe
(testframe.treat <- prepare(treatplan, testframe, varRestriction = newvars))
```


# vtreat the bike rental data

In this exercise you will create one-hot-encoded data frames of the July/August bike data, for use with xgboost later on.

The data frames bikesJuly and bikesAugust are in the workspace.

For your convenience, we have defined the variable vars with the list of variable columns for the model.

```{r}
# The outcome column
(outcome <- "cnt")

# The input columns
(vars <- c("hr", "holiday", "workingday", "weathersit", "temp", "atemp", "hum", "windspeed"))

# Load the package vtreat
library(vtreat)

# Create the treatment plan from bikesJuly (the training data)
treatplan <- designTreatmentsZ(bikesJuly, vars, verbose = FALSE)

# Get the "clean" and "lev" variables from the scoreFrame
(newvars <- treatplan %>%
  use_series(scoreFrame) %>%               
  filter(code %in% c("clean", "lev")) %>%  # get the variables you care about
  use_series(varName))                     # get the varName column

```

# Find the right number of trees for a gradient boosting machine

In this exercise you will get ready to build a gradient boosting model to predict the number of bikes rented in an hour as a function of the weather and the type and time of day. You will train the model on data from the month of July.

The July data is loaded into your workspace. Remember that bikesJuly.treat no longer has the outcome column, so you must get it from the untreated data: bikesJuly$cnt.

You will use the xgboost package to fit the random forest model. The function xgb.cv() uses cross-validation to estimate the out-of-sample learning error as each new tree is added to the model. The appropriate number of trees to use in the final model is the number that minimizes the holdout RMSE.

For this exercise, the key arguments to the xgb.cv() call are:

data: a numeric matrix.
label: vector of outcomes (also numeric).
nrounds: the maximum number of rounds (trees to build).
nfold: the number of folds for the cross-validation. 5 is a good number.
objective: "reg:linear" for continuous outcomes.
eta: the learning rate.
max_depth: depth of trees.
early_stopping_rounds: after this many rounds without improvement, stop.
verbose: 0 to stay silent.

```{r}

# The July data is in the workspace
ls()

# Load the package xgboost
library(xgboost)

# Run xgb.cv
cv <- xgb.cv(data = as.matrix(bikesJuly.treat), 
            label = bikesJuly$cnt,
            nrounds = 100,
            nfold = 5,
            objective = "reg:linear",
            eta = 0.3,
            max_depth = 6,
            early_stopping_rounds = 10,
            verbose = 0   # silent
)

# Get the evaluation log
elog <- cv$evaluation_log

# Determine and print how many trees minimize training and test error
elog %>% 
  summarize(ntrees.train = which.min(train_rmse_mean),   # find the index of min(train_rmse_mean)
            ntrees.test  = which.min(test_rmse_mean))    # find the index of min(test_rmse_mean)

```

# Fit an xgboost bike rental model and predict

In this exercise you will fit a gradient boosting model using xgboost() to predict the number of bikes rented in an hour as a function of the weather and the type and time of day. You will train the model on data from the month of July and predict on data for the month of August.

The datasets for July and August are loaded into your workspace. Remember the vtreat-ed data no longer has the outcome column, so you must get it from the original data (the cnt column).

For convenience, the number of trees to use, ntrees from the previous exercise is in the workspace.

The arguments to xgboost() are similar to those of xgb.cv().

```{r}
# Examine the workspace
ls()

# The number of trees to use, as determined by xgb.cv
ntrees

# Run xgboost
bike_model_xgb <- xgboost(data = as.matrix(bikesJuly.treat), # training data as matrix
                   label = bikesJuly$cnt,  # column of outcomes
                   nrounds = ntrees,       # number of trees to build
                   objective = "reg:linear", # objective
                   eta = 0.3,
                   depth = 6,
                   verbose = 0  # silent
)

# Make predictions
bikesAugust$pred <- predict(bike_model_xgb, as.matrix(bikesAugust.treat))

# Plot predictions vs actual bike rental count
ggplot(bikesAugust, aes(x = pred, y = cnt)) + 
  geom_point() + 
  geom_abline()
```


```{r}

# bikesAugust is in the workspace
str(bikesAugust)

# Calculate RMSE
bikesAugust %>%
  mutate(residuals = cnt - pred) %>%
  summarize(rmse = sqrt(mean(residuals^2)))
```

# Visualize the xgboost bike rental model

You've now seen three different ways to model the bike rental data. For this example, you've seen that the gradient boosting model had the smallest RMSE. To finish up the course, let's compare the gradient boosting model's predictions to the other two models as a function of time.

On completing this exercise, you will have completed the course. Congratulations! Now you have the tools to apply a variety of approaches to your regression tasks.

```{r}
# Print quasipoisson_plot
quasipoisson_plot

# Print randomforest_plot
randomforest_plot

# Plot predictions and actual bike rentals as a function of time (days)
bikesAugust %>% 
  mutate(instant = (instant - min(instant))/24) %>%  # set start to 0, convert unit to days
  gather(key = valuetype, value = value, cnt, pred) %>%
  filter(instant < 14) %>% # first two weeks
  ggplot(aes(x = instant, y = value, color = valuetype, linetype = valuetype)) + 
  geom_point() + 
  geom_line() + 
  scale_x_continuous("Day", breaks = 0:14, labels = 0:14) + 
  scale_color_brewer(palette = "Dark2") + 
  ggtitle("Predicted August bike rentals, Gradient Boosting model")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```
```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
